---
title: "Buff River Inconnu mortality rates and catch curves"
author: "Chelsey Lumb"
format: html
date: "`r Sys.Date()`"
editor: visual
---

Created new quarto file for Buffalo River Inconnu mortality rate estimates because added some data prep/wrangling code to get data file ready

Re-did mortality rate estimates using original ages, not scale to otolith ages used before, because age conversion not right.

```{r}
#| label: note - don't need knitr code chunk at the beginning of quarto file to be able to render 
#| include: false
```

```{r}
#| label: load packages
#| include: false

library(tidyverse) # ggplot2 and purrr part of tidyverse
library(janitor)
library(here)
library(fs)        # tools to work with file-systems, a bit like {here}

library (FSA)
library(knitr)     # to use kable() function to format tables
library(gt)        # to format tables
library(readr)     # to save csv data files to data folder 
```

```{r}
#| label: load data
#| include: false

# Load data and look at data file and data types for wrangling

# Should load raw data and use tally to count catch by year and age in R
# Examples in R4EnviroSci -> week_10_part_1_counting.Rmd


inco_buffriv_original <- read_csv(here("data", "buffriv_inco_catchage.csv"))

str(inco_buffriv_original)

print(inco_buffriv_original)
```

# Prepare data for mortality rate estimates

1)  pivot longer
2)  reorder columns
3)  arrange by year, from earliest to latest (1947 to 2022)
4)  remove years with no ages, 1995 and 2011
5)  replace NAs with zeros
6)  pivot wider again to check catch by year and age matches data in excel (wrangling done right)

```{r}
#| label: data prep
#| include: false
#|

inco <- inco_buffriv_original |> 
  pivot_longer(!age,
               names_to = "year", 
               values_to = "catch") |> 
  select(year, age, catch) |>                                  # reorder columns so year, age, catch
  arrange(year) |>                                             # arrange catch data by year
  filter(year != 1995 & year != 2011) |>                       # filter out years with no age data != 1995 or 2011
  mutate(catch = ifelse(is.na(catch), 0, catch))               # replace nas in catch with zeros
  
#  print(inco)


summary_tbl <- inco %>% 
  pivot_wider(names_from = year, values_from = catch, values_fill = 0) 

# pivot wider, check data right, matches tbl in excel


# readr::write_csv(summary_tbl, here("data", "inco_buffriv_agefreq.csv"))    # save final buff river age freq data file 
```

# Plot data by year, identify descending limb of catch curve

```{r}
#| label: plot data by year, identify descending limb of catch curve 
#| echo: false
#| warning: false
#| message: false

# Add code to get n - number of samples each year for table
  
inco |>   

    filter(year >= 1947 & year <=1979) |>   
 
    ggplot() +
  
  facet_wrap(~ year) +
  geom_point(aes(x = age, y = catch)) +
  
  scale_x_continuous(name="Age (yrs)",expand=expansion(mult=0.02)) +
  scale_y_continuous(name="Catch",expand=expansion(mult=0.02))


inco |>   

    filter(year >= 1980 & year <=1989) |>   
 
    ggplot() +
  
  facet_wrap(~ year) +
  geom_point(aes(x = age, y = catch)) +
  
  scale_x_continuous(name="Age (yrs)",expand=expansion(mult=0.02)) +
  scale_y_continuous(name="Catch",expand=expansion(mult=0.02))


inco |>   

    filter(year >= 1990 & year <=1999) |>   
 
    ggplot() +
  
  facet_wrap(~ year) +
  geom_point(aes(x = age, y = catch)) +
  
  scale_x_continuous(name="Age (yrs)",expand=expansion(mult=0.02)) +
  scale_y_continuous(name="Catch",expand=expansion(mult=0.02))


inco |>   

    filter(year >= 2000 & year <=2009) |>   
 
    ggplot() +
  
  facet_wrap(~ year) +
  geom_point(aes(x = age, y = catch)) +
  
  scale_x_continuous(name="Age (yrs)",expand=expansion(mult=0.02)) +
  scale_y_continuous(name="Catch",expand=expansion(mult=0.02))


inco |>   

    filter(year >= 2010 & year <=2019) |>   
 
    ggplot() +
  
  facet_wrap(~ year) +
  geom_point(aes(x = age, y = catch)) +
  
  scale_x_continuous(name="Age (yrs)",expand=expansion(mult=0.02)) +
  scale_y_continuous(name="Catch",expand=expansion(mult=0.02))


inco |>   

    filter(year >= 2020 & year <=2022) |>   
 
    ggplot() +
  
  facet_wrap(~ year) +
  geom_point(aes(x = age, y = catch)) +
  
  scale_x_continuous(name="Age (yrs)",expand=expansion(mult=0.02)) +
  scale_y_continuous(name="Catch",expand=expansion(mult=0.02))
```

```{r}
#| label: create data file with peak catch and descending limb for each year - code from chatGPT
#| include: false


# Find the age with the highest catch for each year
max_catch_ages <- inco %>%
  group_by(year) %>%
  summarise(max_age = age[which.max(catch)])

# Create a list to store the subsetted data for each year
subset_data_list <- list()

# Loop through each year and subset the data
for (i in 1:nrow(max_catch_ages)) {
  year <- max_catch_ages$year[i]
  max_catch_age <- max_catch_ages$max_age[i]
  subset_data_list[[i]] <- inco[inco$year == year & inco$age >= max_catch_age, ]
}

# Combine the subsetted data for all years into a single data frame
subset_data <- do.call(rbind, subset_data_list)

# Print the subsetted data
print(subset_data)
```

# Plot to check ages included in reduced data frame, ages from peak + descending limb of catch curves

```{r}
#| label: plot descending limbs 
#| echo: false
#| warning: false
#| message: false

subset_data |>  

filter(year >= 1947 & year <=1979) |>   

ggplot(mapping=aes(x=age,y=catch)) +
  geom_point(size=2) +
  geom_line(alpha=0.1,linewidth=1.5) +
  facet_wrap(~ year) +
  theme_bw() + theme(legend.position="none")


subset_data |>  

filter(year >= 1980 & year <=1989) |>   

ggplot(mapping=aes(x=age,y=catch)) +
  geom_point(size=2) +
  geom_line(alpha=0.1,linewidth=1.5) +
  facet_wrap(~ year) +
  theme_bw() + theme(legend.position="none")


subset_data |>  

filter(year >= 1990 & year <=1999) |>   

ggplot(mapping=aes(x=age,y=catch)) +
  geom_point(size=2) +
  geom_line(alpha=0.1,linewidth=1.5) +
  facet_wrap(~ year) +
  theme_bw() + theme(legend.position="none")


subset_data |>  

filter(year >= 2000 & year <=2009) |>   

ggplot(mapping=aes(x=age,y=catch)) +
  geom_point(size=2) +
  geom_line(alpha=0.1,linewidth=1.5) +
  facet_wrap(~ year) +
  theme_bw() + theme(legend.position="none")


subset_data |>  

filter(year >= 2010 & year <=2019) |>   

ggplot(mapping=aes(x=age,y=catch)) +
  geom_point(size=2) +
  geom_line(alpha=0.1,linewidth=1.5) +
  facet_wrap(~ year) +
  theme_bw() + theme(legend.position="none")


subset_data |>  

filter(year >= 2020 & year <=2022) |>   

ggplot(mapping=aes(x=age,y=catch)) +
  geom_point(size=2) +
  geom_line(alpha=0.1,linewidth=1.5) +
  facet_wrap(~ year) +
  theme_bw() + theme(legend.position="none")

```

```{r}
#| label: create nested tibble using year to cyle through each year of data to use in ChapmanRobson function
#| echo: false
#| warning: false
#| message: false

nested_inco_reduced <- subset_data %>% 
  group_by(year) %>% 
  nest()

print(nested_inco_reduced)

nested_inco_reduced$data[[1]]

```

```{r}
#| label: ChapmanRobson catch curve calculations individually by year, to check results from pmap
#| echo: false
#| warning: false
#| message: false


incoccresults <- chapmanRobson(catch~age,data=nested_inco_reduced$data[[38]]) # data frame 1 is year 1947, 38 is 2022
summary(incoccresults)
confint(incoccresults)

# incoccresults 
```

```{r}
#| label: Use pmap to iterate throuh ChapmanRobson catch curve calculations by year
#| echo: false
#| warning: false
#| message: false


# using nested tibble and 'mutate', make a column containing cr_results for each year, name new column `model`
cr_results <- subset_data %>% 
  group_by(year) %>% 
  nest() %>% 
  mutate(model = pmap(list(data),   # tell pmap what element to look at in the list provide in the line above (only one                                         element in list = data)
            
                      ~ chapmanRobson(catch~age,data = ..1 ) # tell pmap what to do with data using ~   data = ..1 because                                                                place in list gave pmap
                      )
         )

cr_results$model[[1]]      # pmap worked! The results for [[1]] match results calculated individually for 1947
confint(cr_results$model[[1]])    # using 'confint' worked to get confidence intervals for S and Z! 

# From https://rdrr.io/cran/FSA/man/chapmanRobson.html, Value - list of model output that is saved, including 
# est A 2x2 matrix that contains the estimates and standard errors for S and Z

cr_results$model[[1]]$est[1] # this gives 1947 estimate for S (est position[1]), if use $est, get S, Z and Std. Errors (df)

cr_results$model[[1]]$n # this gives the number of ages included in the 1947 estimates of S and Z

confint(cr_results$model[[1]]) # this give CIs for S and Z for 1947

confint(cr_results$model[[1]],parm="Z")   # this give CIs for Z only for 1947, but I douln't pull out just Z 95% LCI
        
res <- c(coef(cr_results$model[[1]]),confint(cr_results$model[[1]],parm="S"),confint(cr_results$model[[1]],parm="Z"))
names(res) <- c("S","Z","S.LCI","S.UCI","Z.LCI","Z.UCI")
res[c(1,3,4,2,5,6)]       # worked to pull out S, Z and confidence intervals for 1947!

# this code gets Z and S from values saved in model output - it works, but it's easier to get Z and S and CIs in one tibble

# cr_models_and_results <- cr_results %>%
#  mutate(survival = pmap_dbl(list(model),
#                       ~ round((..1)$est[1], digits = 2)),  # (..1) is place in the list on the line above to use, model,                                                                est is the element in the list `model`, I think, and                                                                       est[1] is the element and the position where S is stored   
#         Z = pmap_dbl(list(model),
#                         ~ round((..1)$est[2], digits = 2)),  # est[2] is the element and the position where Z is stored
#                      
#         n = pmap_dbl(list(model),
#                         ~ (..1)$n),         # number of ages included in the peak + descending limb used to est S and Z  
#         )
 
# this code uses the FSA::ChapmanRobson functions summary and confint to get estimates of Z and S and CIs in one tibble

cr_results_and_cis <- cr_results %>%
  mutate(results = pmap(list(model), 
                     ~ summary(..1)),
         cis = pmap(list(model), 
                     ~ confint(..1))) 

est_and_cis <- cr_results_and_cis %>%
  mutate(z = pmap(list(results), 
                     ~ round((..1)[c(2)], digits = 2)), 
         
         z_95LCI = pmap(list(cis), 
                     ~ round((..1)[c(2)], digits = 2)),
         
         z_95UCI = pmap(list(cis), 
                     ~ round((..1)[c(4)], digits = 2)), 
    
         s = pmap(list(results), 
                     ~ round((..1)[c(1)], digits = 2)),
    
         s_95LCI = pmap(list(cis), 
                     ~ round((..1)[c(1)], digits = 2)),
  
         s_95UCI = pmap(list(cis), 
                     ~ round((..1)[c(3)], digits = 2)) 
         
           ) 

```

```{r}
#| label: unnest tibble with data, model results, and ests of Z, S and CIs, to create a tibble to save with only ests and CIs
#| echo: false
#| warning: false
#| message: false


est_and_cis_b <- est_and_cis %>%       # need to ungroup the data, or R won't let you just select only `plot` and `filename` from tibble
  ungroup() %>%       # if we don't ungroup the data, or R will make you take species and year too, or the data doesn't make sense 
  select(year, z, z_95LCI, z_95UCI, s, s_95LCI, s_95UCI)
  
readr::write_csv(est_and_cis_b, here("results", "buffriv_cr_mort.csv"))               

```

# Plot catch curves showing ages included in mortatliy rate estimates (filled circles) - all years in one figure

```{r}
#| label: plot catch curves all years
#| echo: false
#| warning: false
#| message: false

plot_cc_all_yrs <-

ggplot() +
  geom_point(dat=inco,mapping=aes(x=age,y=catch),
             pch=21,size=2) +
  geom_point(dat=subset_data,mapping=aes(x=age,y=catch),
             pch=21,size=2,fill="black") +
 # geom_smooth(dat=incoccresults,mapping=aes(x=age,y=catch),
 #            method=lm) +
  scale_x_continuous(name="Age (yrs)",expand=expansion(mult=0.02)) +
  scale_y_continuous(name="Catch",expand=expansion(mult=0.02)) +
#  scale_color_manual(values=c("Fall"="black","Spring"="gray60"),
#                     aesthetics=c("color","fill")) +
  facet_wrap(~year, strip.position="right") +
  theme_bw() +
  theme(panel.grid.major=element_blank(),
        legend.position=c(1,1),
        legend.justification=c(1.1,1.1),
        legend.title=element_blank(),
        legend.background=element_blank(),
        strip.text=element_text(face="bold"))

plot(plot_cc_all_yrs)

ggsave(here("figures", "plot_cc_all_yrs.pdf"), plot_cc_all_yrs,
       width = 190, height = 120, units = "mm")

```

# Plot catch curves in year groups, to better show ages included in mortatliy rate estimates (filled circles)

```{r}
#| label: plot catch curves by years grouped to see plots better
#| echo: false
#| warning: false
#| message: false

# this code is modified from Derek Ogle's fishR post https://fishr-core-team.github.io/fishR/blog/posts/2023-4-24_Multiple_CatchCurves/

inco_filtered <- subset(inco, year >= 1947 & year <= 1989) 
   
subset_data_filtered <- subset(subset_data, year >= 1947 & year <= 1989)   

plot_cc_buff_1947_1989 <-

ggplot() +
  geom_point(dat=inco_filtered,mapping=aes(x=age,y=catch),
             pch=21,size=2) +
  geom_point(dat=subset_data_filtered,mapping=aes(x=age,y=catch),
             pch=21,size=2,fill="black") +
 # geom_smooth(dat=incoccresults,mapping=aes(x=age,y=catch),
 #            method=lm) +
  scale_x_continuous(name=NULL,expand=expansion(mult=0.02),
                     limits=c(0,25),breaks=seq(0,25,5)) +
  scale_y_continuous(name="Catch",expand=expansion(mult=0.02), 
                     limits=c(0,200),breaks=seq(0,200,50)) +
#  scale_color_manual(values=c("Fall"="black","Spring"="gray60"),
#                     aesthetics=c("color","fill")) +
  facet_wrap(~year, strip.position="right") +
  theme_bw() +
  theme(panel.grid.major=element_blank(),
        legend.position=c(1,1),
        legend.justification=c(1.1,1.1),
        legend.title=element_blank(),
        legend.background=element_blank(),
        strip.text=element_text(face="bold"))

plot(plot_cc_buff_1947_1989)

ggsave(here("figures", "plot_cc_buff_1947_1989.jpg"), plot_cc_buff_1947_1989,
       width = 190, height = 120, units = "mm")


inco_filtered <- subset(inco, year >= 1990 & year <= 2022) 
   
subset_data_filtered <- subset(subset_data, year >= 1990 & year <= 2022)   

plot_cc_buff_1990_2022 <-

ggplot() +
  geom_point(dat=inco_filtered,mapping=aes(x=age,y=catch),
             pch=21,size=2) +
  geom_point(dat=subset_data_filtered,mapping=aes(x=age,y=catch),
             pch=21,size=2,fill="black") +
 # geom_smooth(dat=incoccresults,mapping=aes(x=age,y=catch),
 #            method=lm) +
  scale_x_continuous(name="Age (yrs)",expand=expansion(mult=0.02),
                     limits=c(0,25),breaks=seq(0,25,5)) +
  scale_y_continuous(name="Catch",expand=expansion(mult=0.02), 
                     limits=c(0,200),breaks=seq(0,200,50)) +
#  scale_color_manual(values=c("Fall"="black","Spring"="gray60"),
#                     aesthetics=c("color","fill")) +
  facet_wrap(~year, strip.position = ("right")) +
  theme_bw() +
  theme(panel.grid.major=element_blank(),
        legend.position=c(1,1),
        legend.justification=c(1.1,1.1),
        legend.title=element_blank(),
        legend.background=element_blank(),
        strip.text=element_text(face="bold"))

plot(plot_cc_buff_1990_2022)

ggsave(here("figures", "plot_cc_buff_1990_2022.jpg"), plot_cc_buff_1990_2022,
       width = 190, height = 120, units = "mm")


```

# Load decadal data for mortality rate estimates

```{r}
#| label: load data for buffalo river decadal mortality rate estimates
#| include: false

# Load data and look at data file and data types for wrangling

# Should load raw data and use tally to count catch by year and age in R
# Examples in R4EnviroSci -> week_10_part_1_counting.Rmd


inco_buffriv_decade <- read_csv(here("data", "buffriv_decade_catchage.csv"))

str(inco_buffriv_decade)

print(inco_buffriv_decade)

```

# Prepare data for decadal mortality rate estimates

```{r}
#| label: data prep for decadal data 
#| include: false
#|

inco <- inco_buffriv_decade |> 
  pivot_longer(!age,
               names_to = "year",                              # in this case year means decade
               values_to = "catch") |> 
  select(year, age, catch) |>                                  # reorder columns so year, age, catch
  arrange(year) |>                                             # arrange catch data by year
  mutate(catch = ifelse(is.na(catch), 0, catch))               # replace nas in catch with zeros
  
#  print(inco)


summary_tbl <- inco %>% 
  pivot_wider(names_from = year, values_from = catch, values_fill = 0) 

```

```{r}
#| label: plot data by decade, identify descending limb of catch curve 
#| echo: false
#| warning: false
#| message: false

# Add code to get n - number of samples each year for table
  
inco |>   

    ggplot() +
  
  facet_wrap(~ year) +
  geom_point(aes(x = age, y = catch)) +
  
  scale_x_continuous(name="Age (yrs)",expand=expansion(mult=0.02)) +
  scale_y_continuous(name="Catch",expand=expansion(mult=0.02))

```

# For decadal data create data file with peak catch and descending limb

```{r}
#| label: for decadal data create data file with peak catch and descending limb - code from chatGPT
#| include: false


# Find the age with the highest catch for each year
max_catch_ages <- inco %>%
  group_by(year) %>%
  summarise(max_age = age[which.max(catch)])

# Create a list to store the subsetted data for each year
subset_data_list <- list()

# Loop through each year and subset the data
for (i in 1:nrow(max_catch_ages)) {
  year <- max_catch_ages$year[i]
  max_catch_age <- max_catch_ages$max_age[i]
  subset_data_list[[i]] <- inco[inco$year == year & inco$age >= max_catch_age, ]
}

# Combine the subsetted data for all years into a single data frame
subset_data <- do.call(rbind, subset_data_list)

# Print the subsetted data
print(subset_data)
```

# Plot to `subset_data` to check ages included in reduced data frame, ages from peak + descending limb of catch curves for decades

```{r}
#| label: plot descending limbs for decadal data
#| echo: false
#| warning: false
#| message: false

subset_data |>  
  

ggplot(mapping=aes(x=age,y=catch)) +
  geom_point(size=2) +
  geom_line(alpha=0.1,linewidth=1.5) +
  facet_wrap(~ year) +
  theme_bw() + theme(legend.position="none")

```

# For decadal data, create nested tibble to use year (first year of decade) to estimate mortality

```{r}
#| label: create nested tibble using year (first year of decade) to cyle through decade and use in ChapmanRobson function
#| echo: false
#| warning: false
#| message: false

nested_inco_reduced <- subset_data %>% 
  group_by(year) %>% 
  nest()

print(nested_inco_reduced)

nested_inco_reduced$data[[1]]

```

# Check pmap working as expected by checking results

```{r}
#| label: ChapmanRobson catch curve calculations individually by decade (labelled with first year), to check results from pmap
#| echo: false
#| warning: false
#| message: false


incoccresults <- chapmanRobson(catch~age,data=nested_inco_reduced$data[[8]]) # data frame 1 is decade 1940's, 8 is the 2020's
summary(incoccresults)
confint(incoccresults)

# incoccresults 
```

# For decadal data, use pmap to calculate mortality rates by decade

```{r}
#| label: Use pmap to iterate throuh ChapmanRobson catch curve calculations by decade (labelled with first year of decade)
#| echo: false
#| warning: false
#| message: false


# using nested tibble and 'mutate', make a column containing cr_results for each year, name new column `model`
cr_results <- subset_data %>% 
  group_by(year) %>% 
  nest() %>% 
  mutate(model = pmap(list(data),   # tell pmap what element to look at in the list provide in the line above (only one                                         element in list = data)
            
                      ~ chapmanRobson(catch~age,data = ..1 ) # tell pmap what to do with data using ~   data = ..1 because                                                                place in list gave pmap
                      )
         )

cr_results$model[[1]]      # pmap worked! The results for [[1]] match results calculated individually for the 1940's
confint(cr_results$model[[1]])    # using 'confint' worked to get confidence intervals for S and Z! 

# From https://rdrr.io/cran/FSA/man/chapmanRobson.html, Value - list of model output that is saved, including 
# est A 2x2 matrix that contains the estimates and standard errors for S and Z

cr_results$model[[1]]$est[1] # this gives 1947 estimate for S (est position[1]), if use $est, get S, Z and Std. Errors (df)

cr_results$model[[1]]$n # this gives the number of ages included in the 1947 estimates of S and Z

confint(cr_results$model[[1]]) # this give CIs for S and Z for 1947

confint(cr_results$model[[1]],parm="Z")   # this give CIs for Z only for 1947, but I douln't pull out just Z 95% LCI
        
res <- c(coef(cr_results$model[[1]]),confint(cr_results$model[[1]],parm="S"),confint(cr_results$model[[1]],parm="Z"))
names(res) <- c("S","Z","S.LCI","S.UCI","Z.LCI","Z.UCI")
res[c(1,3,4,2,5,6)]       # worked to pull out S, Z and confidence intervals for 1947!

# this code gets Z and S from values saved in model output - it works, but it's easier to get Z and S and CIs in one tibble

# cr_models_and_results <- cr_results %>%
#  mutate(survival = pmap_dbl(list(model),
#                       ~ round((..1)$est[1], digits = 2)),  # (..1) is place in the list on the line above to use, model,                                                                est is the element in the list `model`, I think, and                                                                       est[1] is the element and the position where S is stored   
#         Z = pmap_dbl(list(model),
#                         ~ round((..1)$est[2], digits = 2)),  # est[2] is the element and the position where Z is stored
#                      
#         n = pmap_dbl(list(model),
#                         ~ (..1)$n),         # number of ages included in the peak + descending limb used to est S and Z  
#         )
 
# this code uses the FSA::ChapmanRobson functions summary and confint to get estimates of Z and S and CIs in one tibble

cr_results_and_cis <- cr_results %>%
  mutate(results = pmap(list(model), 
                     ~ summary(..1)),
         cis = pmap(list(model), 
                     ~ confint(..1))) 

est_and_cis <- cr_results_and_cis %>%
  mutate(z = pmap(list(results), 
                     ~ round((..1)[c(2)], digits = 2)), 
         
         z_95LCI = pmap(list(cis), 
                     ~ round((..1)[c(2)], digits = 2)),
         
         z_95UCI = pmap(list(cis), 
                     ~ round((..1)[c(4)], digits = 2)), 
    
         s = pmap(list(results), 
                     ~ round((..1)[c(1)], digits = 2)),
    
         s_95LCI = pmap(list(cis), 
                     ~ round((..1)[c(1)], digits = 2)),
  
         s_95UCI = pmap(list(cis), 
                     ~ round((..1)[c(3)], digits = 2)) 
         
           ) 

```

# For decadal data, unnest tibble to create tibble with mortality rate estimates and CIs

```{r}
#| label: unnest tibble with decadal data, model results, ests of Z, S and CIs, to create a tibble to save with only ests and CIs
#| echo: false
#| warning: false
#| message: false


est_and_cis_b <- est_and_cis %>%       # need to ungroup the data, or R won't let you just select only `plot` and `filename` from tibble
  ungroup() %>%       # if we don't ungroup the data, or R will make you take species and year too, or the data doesn't make sense 
  select(year, z, z_95LCI, z_95UCI, s, s_95LCI, s_95UCI)
  
readr::write_csv(est_and_cis_b, here("results", "buffriv_cr_mort.csv"))               

```

# For decades, plot catch curves showing ages included in mortatliy rate estimates (filled circles)

```{r}
#| label: plot catch curves by decade, year is first year of decade
#| echo: false
#| warning: false
#| message: false

plot_cc_decade <-

ggplot() +
  geom_point(dat=inco,mapping=aes(x=age,y=catch),
             pch=21,size=2) +
  geom_point(dat=subset_data,mapping=aes(x=age,y=catch),
             pch=21,size=2,fill="black") +
 # geom_smooth(dat=incoccresults,mapping=aes(x=age,y=catch),
 #            method=lm) +
  scale_x_continuous(name="Age (yrs)",expand=expansion(mult=0.02)) +
  scale_y_continuous(name="Catch",expand=expansion(mult=0.02)) +
#  scale_color_manual(values=c("Fall"="black","Spring"="gray60"),
#                     aesthetics=c("color","fill")) +
  facet_wrap(~year) +
  theme_bw() +
  theme(panel.grid.major=element_blank(),
        legend.position=c(1,1),
        legend.justification=c(1.1,1.1),
        legend.title=element_blank(),
        legend.background=element_blank(),
        strip.text=element_text(face="bold"))

plot(plot_cc_decade)

ggsave(here("figures", "plot_cc_decade.pdf"), plot_cc_decade,
       width = 190, height = 120, units = "mm")

```
