---
title: "GSL 2023 LKTR East Arm mort rate calcs"
format: html
editor: visual
---

New quarto file to update Great Slave Lake Lake Trout mortality rate estimate from East Arm, using 2023 data from LKDFN (oto ages, n=128 ages, 72 missing oto from one fisher) (no Main Basin/KFN LKTR samples from community sampling in 2023 b/c of wildfire evaculations)

Coped from "GSL Inconnu mortality rates and catch curves Quarto file - the quatro file was for Slave River Inconnu for stock assessment working paper

```{r}
#| label: note - don't need knitr code chunk at the beginning of quarto file to be able to render 
#| include: false
```

```{r}
#| label: load packages
#| include: false

library(tidyverse) # ggplot2 and purrr part of tidyverse
library(janitor)
library(here)
library(fs)        # tools to work with file-systems, a bit like {here}

library (FSA)
library(knitr)     # to use kable() function to format tables
library(gt)        # to format tables
library(readr)     # to save csv data files to data folder 
```

```{r}
#| label: load data
#| results: hide
#| echo: false
#| warning: false
#| message: false
#| include: false

## recommend using the comment-based syntax (#|) vs. chunk options on the first line (e.g. {r, load packages, include=FALSE}) to make documents more portable and consistent across execution engines https://quarto.org/docs/tools/rstudio.html

# Should load raw data and tally catch by age in R

lktr <- read_csv(here("data", "gsl_2023lktr_agefreq.csv"))

str(lktr)

print(lktr)
```

# Load and look at summary of data, age range and number of observations of age by year

```{r}
#| label: explore data 
#| echo: false
#| warning: false
#| message: false

# Add code to give me n total number of fish sampled per year, for mort rate table

lktr |>  
  group_by(year) |>
  summarize(agerng=max(age)-min(age)+1,
            agesobs=n()) 
```

# Visually select years to include in descending limb

Plot to check ages included in descending limb - should include the peak age, the age when fish have just become fully vulnerable to the gear, and the descending right limb

```{r}
#| label: plot data by year, identify descending limb of catch curve 
#| echo: false
#| warning: false
#| message: false

# From FishR Vignette - Catch Curve Estimates of Mortality, March 2, 2013, plot scatterplot of age vs log(10)Catch (or catch?)
# this is the catch curve

# From Derek Ogle's fishR post https://fishr-core-team.github.io/fishR/blog/posts/2023-4-24_Multiple_CatchCurves/
# In general, instantaneous mortality (Z) is only estimated from the slope of the “descending limb” of the catch curve
# Use plots below to identify the “descending limb”


lktr |>   
  ggplot() +
  facet_wrap(~ year) +
  geom_point(aes(x = age, y = catch)) +
  
  scale_x_continuous(name="Age (yrs)",expand=expansion(mult=0.02)) +
  scale_y_continuous(name="Catch",expand=expansion(mult=0.02))

```

# Subset data to only include peak + decsending limb of catch curve in data file for mortality rate calcuation

```{r}
#| label: create data file with peak catch and descending limb from visually inspecting catch curve 
#| include: false

# For East Arm 2023 lktr data from LKDFN, max age was 12 years (ten lktr)
# ended up truncating catch data to age 41 and younger, to get mort rate more in line with recent years
# in Natural Mortality Rate Calculator, used age 42 for max age (longevity) for East Arm, and M median ~ 0.16, M mean ~ 0.24
# used this mort rate estimate to update east arm mort rate for 2023 for GSLAC May 2024

subset_data <- lktr |>   
  filter(age >= 12, age <= 41)

# Print the subsetted data
print(subset_data)

```

# ChapmanRobson catch curve calculations individually for one year, 2023 for East Arm LKTR

```{r}
#| label: ChapmanRobson catch curve calculations individually for one year, 2023 for East Arm LKTR
#| echo: false
#| warning: false
#| message: false


lktrccresults <- chapmanRobson(catch~age,data=subset_data) 
summary(lktrccresults)
confint(lktrccresults)

# lktrccresults
```

\`\`\`
